% Please paste the bib entries of papers published outside NLP 
% We will use a program to clean up them and include these papers in the ref.bib later
% Use the following pre-defined conference name if possible.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%        JOURNALS           %%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


@string{AI = {Artificial Intelligence}}

@string{CACM = {Communications of the ACM}}

@string{CSL = {Computer Speech and Language}}

% @string{CL = {Computational Linguistics}}

@string{InfCtrl = {Information and Control}}

@string{IT = {IEEE Transactions on information theory}}

@string{JACM = {Journal of the ACM}}

@string{JAIR = {Journal of AI Research}}

@string{JMLR = {Journal of Machine Learning Research}}

@string{ML = {Machine Learning}}

@string{NLE = {Journal of Natural Language Engineering}}

@string{MM = {IEEE Transactions on Multimedia}}

@string{PAMI = {IEEE Transactions on Pattern Analysis and Machine Intelligence}}

@string{SIJAD = {SIAM Journal of Algebraic and Discrete Methods}}

@string{SIJC = {SIAM Journal of Computing}}

@string{TASSP = {IEEE Transactions on Acoustics, speech, and Signal Processing}}

@string{TASSP = {IEEE Transactions on Acoustics, speech, and Signal Processing}}

@string{TCS = {Theoretical Computer Science}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%       CONFERENCES         %%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


@string{AAAI= {Proceedings of the National Conference on Artificial Intelligence (AAAI)}}

@string{ANLP = {Proc. of ACL Conference on Applied Natural Language Processing}}

@string{ARPA = {Proc. of the ARPA Workshop on Human Language Technology}}

@string{ACCV = {Proceedings of the Asian Conference on Computer Vision (ACCV)}}

@string{AISTAT = {Proceedings of the International Workshop on Artificial Intelligence and Statistics}}

%@string{COLING = {Proc.  the International Conference on Computational Linguistics (COLING)}}

%@string{ACL = {Proc. of the Annual Meeting of the Association of Computational Linguistics (ACL)}}

@string{COLT = {Proc. of the Annual ACM Workshop on Computational Learning Theory (COLT)}}

%@string{CoNLL = {Proc. of the Annual Conference on Computational Natural Language Learning (CoNLL)}}

@string{CVPR = {The IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}}

@string{ECML = {Proc. of the European Conference on Machine Learning (ECML)}}

@string{FOCS = {IEEE Symp. of Foundation of Computer Science}}

@string{ECCV = {Proc. of the European Conference on Computer Vision (ECCV)}}

@string{IAAI= {Proceedings of the National Conference on Innovative Applications of Artificial Intelligence (IAAI)}}

@string{ICML = {Proc. of the International Conference on Machine Learning (ICML)}}

@string{ICASSP = {Proc. of ICASSP}}

@string{IJCAI = {Proc. of the International Joint Conference on Artificial Intelligence (IJCAI)}}

%@string{IJCNLP = {Proc. of the International Joint Conference on Natural Language Processing (IJCNLP)}}

@string{ISMB = {The International Conference on Intelligent Systems for Molecular Biology}}

%@string{NAACL = {Proc. of the Annual Meeting of the North American Association of Computational Linguistics (NAACL)}}

@string{NeurIPS = {The Conference on Advances in Neural Information Processing Systems (NeurIPS)}}

@string{SIGIR = {Proc. of International Conference on Research and Development in Information Retrieval, SIGIR}}

@string{SIGDAT = {Proc. of the Conference on Empirical Methods for Natural Language Processing (EMNLP)}}

%@string{EMNLP = {Proc. of the Conference on Empirical Methods for Natural Language Processing (EMNLP)}}

@string{STOC = {ACM Symp. of the Theory of Computing}}

@string{JACM = {Journal of the ACM}}

@string{WWW = {The International World Wide Web Conference}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%  Begin Publications List  %%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@inproceedings{bolukbasi2016man,
  title={Man is to computer programmer as woman is to homemaker? debiasing word embeddings},
  author={Bolukbasi, Tolga and Chang, Kai-Wei and Zou, James Y and Saligrama, Venkatesh and Kalai, Adam T},
  booktitle=NeurIPS,
  year={2016}
}
